### 2025-09-25 paper/sec/authoring-workflow.tex

\item \textbf{High-level Authoring workflow.} The system then enters the human-in-the loop authoring workflow
shown in Figure~\ref{fig:interpretation-agent}, where the author interacts with the \InterpretationAgent. The
system waits for the author to select a fragment of text $s$ to interpret (perhaps previously highlighted by
the \SuggestionAgent). The system then attempts to generate \mdnote{I changed ``generates'' to ``generate''} a candidate Fluid expression $e$ using the
closed-loop synthesis step (3) below. If code synthesis succeeds with an expression $e$, the system proceeds
to the manual validation step (4) below. If the synthesis step fails with no expression, no remedial action is
possible; this is considered an unsuccessful path through the workflow and returns the system to the entry
state. Otherwise the synthesis step produces an expression $e$ which evaluates to a mismatched string $s' \neq
s$ outcome, and the user can choose to manually abort and return to the entry state, or optionally to
\emph{revise the goal}, replacing $s$ with $s'$ in the target document and retaining $e$ as the candidate
expression. This is intended to cover the situation where the author has made a claim which is
\emph{incorrect}, and the data set and surrounding natural language have led the LLM to synthesise an
expression which generates a different value from the one specified by the user.

@@

\subsection{Prompt Design}
\label{sec:prompt-design}

\paragraph{System Prompt.}
For the Interpretation Assistant, the system prompt guides the LLM in replacing placeholder tags in the
supplied paragraph with executable Fluid expressions. It includes the following information about the document
under construction, the exact task to perform, and constraints on the expected output. The full system prompt
is given in \appref{system-prompt:interpretation-agent}.

\begin{itemize}
\item \textbf{Input structure:} summarises the imported datasets, modules, auxililiary definitions in scope in
the current file, the current Fluid representation of the target paragraph with \kw{[REPLACE …]} tag
indicating the text fragment to replace, plus the full text for the paragraph.
\item \textbf{Task description:} description of the LLM task, namely to identify \kw{[REPLACE …]} placeholder
and generate Fluid expression that produces target string using supplied dataset and definitions in scope.
\item \textbf{Output constraints:} specify that the LLM should return a syntactically valid Fluid expression,
with no extraneous content (such as comments).
\end{itemize}

\rpnote{Now something about the rest of the prompt.}

>>>>

\item \textbf{High-level Authoring workflow.} The system then enters the human-in-the loop authoring workflow
shown in Figure~\ref{fig:interpretation-agent}, where the author interacts with the \InterpretationAgent. The
system waits for the author to select a fragment of text $s$ to interpret (perhaps previously highlighted by
the \SuggestionAgent). The system then attempts to generate a candidate Fluid expression $e$ using the
closed-loop synthesis step (3) below. If code synthesis succeeds with an expression $e$, the system proceeds
to the manual validation step (4) below. If the synthesis step fails with no expression, no remedial action is
possible; this is considered an unsuccessful path through the workflow and returns the system to the entry
state. Otherwise the synthesis step produces an expression $e$ which evaluates to a mismatched string $s' \neq
s$ outcome, and the user can choose to manually abort and return to the entry state, or optionally to
\emph{revise the goal}, replacing $s$ with $s'$ in the target document and retaining $e$ as the candidate
expression. This is intended to cover the situation where the author has made a claim which is
\emph{incorrect}, and the data set and surrounding natural language have led the LLM to synthesise an
expression which generates a different value from the one specified by the user.

@@

\subsection{The InterpertationAgent}
\label{sec:interpretation-agent}

\cdnote{I integrated the prompt description in the description of the InterpretationAgentv (unsure if this is the best plece) -- the prompt description seemed to basic (it's commented if you want to revert)}

The InterpretationAgent is guided by a structured system prompt that
frames code generation as a precise replacement task. The model
receives the imported datasets, helper modules, and the current Fluid
representation of the paragraph, in which a text fragment is marked
with [REPLACE …]. Its task is to substitute this placeholder with a
Fluid expression that evaluates exactly to the target string,
reconstructing quantitative or comparative claims as dataset queries
where appropriate. To ensure integration with the workflow, the output
must consist solely of a syntactically valid Fluid expression, with no
additional commentary. This focused design constrains the model while
providing enough context to generate expressions that are both
data-grounded and immediately executable; the full prompt is given in~\appref{system-prompt:interpretation-agent}.

%\paragraph{System Prompt.}
%For the Interpretation Assistant, the system prompt guides the LLM in replacing placeholder tags in the
%supplied paragraph with executable Fluid expressions. It includes the following information about the document
%under construction, the exact task to perform, and constraints on the expected output. The full system prompt
%is given in \appref{system-prompt:interpretation-agent}.

%\begin{itemize}
%\item \textbf{Input structure:} summarises the imported datasets, modules, auxililiary definitions in scope in
%the current file, the current Fluid representation of the target paragraph with \kw{[REPLACE …]} tag
%indicating the text fragment to replace, plus the full text for the paragraph.
%\item \textbf{Task description:} description of the LLM task, namely to identify \kw{[REPLACE …]} placeholder
%and generate Fluid expression that produces target string using supplied dataset and definitions in scope.
%\item \textbf{Output constraints:} specify that the LLM should return a syntactically valid Fluid expression,
%with no extraneous content (such as comments).
%\end{itemize}

%\rpnote{Now something about the rest of the prompt.}
